\documentclass{article}
\usepackage{bookmark}
\usepackage{color}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{amsfonts}
\begin{document}
\begin{itemize}
\item Where is the CPU hidden, and why?\\
CPU is hidden on the motherboard with a shield covering. It is on the motherboard because it functions to control it, and it is shielded in order to protect it from the possible damage fron the external.
\item What are the North and South bridges?\\
North bridge is a chip on the mother board which serves to perform high speed communication between CPU and RAM, PCI. South bridge is also a chip on the motherboard, but it mainly function to build communication between CPU and I/O devices.
\item How are the North and South bridges connected together?\\
North bridge connects the southbridge and CPU to offer communication between them.
\item What is the BIOS?\\
BIOS is a firmware on computer which offers basic communication method to the hardwares on the computer to the user and operating systems.
\item Take out the CPU, rotate it and try to plug it back in a different position, is that working?\\
It does not work. The CPU cannot fit into the socket.
\item Explain what overclocking is?\\
Overclocking is the action that makes computer run faster than it is supposed to run.
\item What are pins on a PCI/PCI-e card and what are they used for?\\
They are connector pinout and they serves to create communication between the computer and the peripherals connected.
\item Before PCI-e became a common standard many graphics cards were using Accelerated Graphics Port (AGP), explain why. \\
It connects graphic card and system main memory directly so higher speed can be reached. What's more, it can use system main memory to help if the memory in graphic card is not enough.
\end{itemize}
\end{document}